### 2017-04-28 introduction.tex
Add files via upload

@@

Geometric biases in TIR remote sensing of the urban surface are the result of urban modification of surface structure and thermal and radiative properties. Relative to typical non-urban and rural terrain, urban development adds significant 3-dimensionality to the surface. This added complexity results in undersampling of the surface by narrow-FOV remote sensors. A narrow-FOV sensor, by sampling surface 3-dimensionality in 2-dimensions, "sees" a different assemblage of urban surfaces depending on its viewing direction, resulting in a geometric bias towards some arrangement of facets. I.e. viewing from the nadir, a narrow-FOV sensor sees the urban surface as an array of rooftops and roads, the same sensor viewing perpendicular to the surface sees wall facets exclusively, and one viewing from some off nadir angle sees some array of walls, rooftops, and roads depending on its orientation.

In addition, the convoluted 3-dimensional structure of the urban surface modifies sunlit/shading regimes, resulting in strong micro-scale spatiotemporal contrasts in urban T\textsubscript{surf}, which depend on surface-sun geometry. These microscale variations in urban T\textsubscript{surf} are often amplified by significant directional contrasts in the thermal admittance of common urban materials, which determines the diurnal amplitude of T\textsubscript{surf} for a given facet. Thus, when viewed from a narrow-FOV remote sensor with some inherent geometric bias, urban T\textsubscript{surf} is directionally dependent - constituting an "effective anisotropy" of urban T\textsubscript{surf}, shown in Figure \ref{anisot}. The qualifier "effective" is used to differentiate directional contrasts in urban T\textsubscript{surf} that arise from a city's 3-dimensional surface structure from those resulting from the non-Lambertian nature of individual urban facets (e.g. walls, rooftops, or roads). The magnitude of urban effective anisotropy can reach up to 10 \si{\kelvin} and is highly dependent on surface-sensor-sun geometry, surface structure, and urban materials \citep{Krayenhoff2016, Voogt1997}.

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,
	height=7in,
	keepaspectratio]{anisot}
	\caption{A narrow-FOV sensor viewing an idealized urban surface from two angles. Left: viewing the surface approximately perpendicular to the sun's angle. Right: viewing the surface approximately parallel to the sun's angle. The two viewing angles described in the left and right panels yield different remote sensed T\textsubscript{surf} by sampling different arrangements of sunlit and shaded features. Both will deviate from an area weighted "complete" urban T\textsubscript{surf}.}
	\label{anisot}
\end{figure}

@@

Prompted by these shortcomings in the remote sensed urban T\textsubscript{surf} record, this thesis introduces a method to provide geometrically representative, temporally continuous urban T\textsubscript{surf} for sUHI analysis to address the following questions:

\begin{itemize}
	\item What is the nature of urban surface temperature when viewed from a hemispherical downward-facing radiometer? And how does it relate to urban temperatures derived from other methods for urban surface temperature retrieval?
	\item What is the diurnal and seasonal nature of the surface urban heat island effect?
\end{itemize}

@@

\begin{enumerate}
	\item Developed and evaluated a method to retrieve atmospherically correction hemispherical radiometric urban surface temperatures from time-continuous measurements of upwelling longwave radiation.
	\item Compared urban surface temperatures and surface urban heat island magnitudes retrieved using the method to common remote sensed representations of the urban surface.
	\item Derived an eight month climatology of hemispherical urban surface temperatures to observe seasonal and diurnal patterns of the surface urban heat island effect.
\end{enumerate}

\section{The structure of the following sections}

The following two papers make up the body of the thesis, read them you fuck.

>>>>

\begin{bibunit}

\rhead{\thepage}

@@

Geometric biases in TIR remote sensing of the urban surface are the result of urban modification of surface structure and thermal and radiative properties. Relative to typical non-urban and rural terrain, urban development adds significant 3-dimensionality to the surface. This added complexity results in undersampling of the surface by narrow-FOV remote sensors. A narrow-FOV sensor, by sampling surface 3-dimensionality in 2-dimensions, "sees" a different assemblage of urban surfaces depending on its viewing direction, resulting in a geometric bias towards some arrangement of facets. I.e. viewing from the nadir, a narrow-FOV sensor sees the urban surface as an array of rooftops and roads, the same sensor viewing the from an oblique angle sees some array of walls, rooftops, and roads depending on its orientation. For a sensor in the nadir, increasing FOV introduces sampling of vertical features. To illustrate how sensor-surface geometry influences sampling of the urban surface by narrow- and wide-FOV sensors, Figure \ref{model} shows FOVs for the three sensor orientation/type combinations.The vast majority of urban thermal remote sensing is done via a narrow-FOV sensor in the nadir.

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,
	height=7in,
	keepaspectratio]{model}
	\caption{Projected FOVs for a narrow-FOV sensor at nadir and oblique angles, and a wide-FOV hemispherical sensor viewing an idealized urban array with building width T\textit{H}, height 2\textit{H}, and inter element spacing textit{H}. Figure from \cite{Adderley2015}.}
	\label{model}
\end{figure}

In addition to modifying how a remote sensor samples the surface, the convoluted 3-dimensional structure of the urban surface modifies sunlit/shading regimes, resulting in strong micro-scale spatiotemporal contrasts in urban T\textsubscript{surf}, which depend on surface-sun geometry. These microscale variations in urban T\textsubscript{surf} are often amplified by significant directional contrasts in the thermal admittance of common urban materials, which determines the diurnal amplitude of T\textsubscript{surf} for a given facet. Thus, when viewed from a narrow-FOV remote sensor with some inherent geometric bias, urban T\textsubscript{surf} is directionally dependent - constituting an "effective anisotropy" of urban T\textsubscript{surf}, shown in Figure \ref{anisot}. The qualifier "effective" is used to differentiate directional contrasts in urban T\textsubscript{surf} that arise from a city's 3-dimensional surface structure from those resulting from the non-Lambertian nature of individual urban facets (e.g. walls, rooftops, or roads). The magnitude of urban effective anisotropy can reach up to 10 \si{\kelvin} and is highly dependent on surface-sensor-sun geometry, surface structure, and urban materials \citep{Krayenhoff2016, Voogt1997}.

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,
	height=7in,
	keepaspectratio]{anisot}
	\caption{A narrow-FOV sensor viewing an idealized urban surface from two angles. Left: viewing the surface approximately perpendicular to the sun's angle. Right: viewing the surface approximately parallel to the sun's angle. The two viewing angles yield different remote sensed T\textsubscript{surf} by sampling different arrangements of sunlit and shaded features. Both will deviate from an area weighted "complete" urban T\textsubscript{surf}.}
	\label{anisot}
\end{figure}

@@

Prompted by these shortcomings in the remote sensed urban T\textsubscript{surf} record, and in an effort to better understand the temporal and geometric aspects of sUHI, this thesis introduces a method to provide hemispherical, temporally continuous urban T\textsubscript{surf} for sUHI analysis to address the following questions:

\begin{enumerate}
	\item What is the nature of urban surface temperature when viewed from a hemispherical downward-facing radiometer? And how does it relate to urban temperatures derived from other methods for urban surface temperature retrieval?
	\item What is the diurnal and seasonal nature of the surface urban heat island effect?
\end{enumerate}

@@

\begin{itemize}
	\item Developed and evaluated a method to retrieve atmospherically correction hemispherical radiometric urban surface temperatures from time-continuous measurements of upwelling longwave radiation.
	\item Compared urban surface temperatures and surface urban heat island magnitudes retrieved using the method to common remote sensed representations of the urban surface.
	\item Derived an eight month climatology of hemispherical urban surface temperatures to observe seasonal and diurnal patterns of the surface urban heat island effect.
\end{itemize}

The following two chapters address questions one and two respectively. Chapter \ref{paper1} details and evaluates a method to retrieve atmospherically corrected, hemispherical urban T\textsubscript{surf} from time-continuous measurements of upwelling longwave radiation. Chapter \ref{paper2} explores the temporal and geometric nature of sUHI through an eight month climatological analysis of hemispherical sUHI and compares sUHI magnitudes from several representations of the urban surface.

\cleardoublepage 
\phantomsection  
\renewcommand*{\bibname}{References}
\addcontentsline{toc}{section}{\textbf{References}}

\putbib
\end{bibunit}

### 2017-04-28 paper1.tex
Add files via upload

\chapter{A hemispherical atmospheric correction method to derive time-continuous urban surface temperature}\label{paper1}

@@

@@

>>>>

\begin{bibunit}

\rhead{\thepage}

\chapter{An atmospheric correction method to derive hemispherical time-continuous urban surface temperature}\label{paper1}

@@

\section{A practical parameterization}

To save computational time and facilitate broader use of the method, a parameterization scheme was developed to simplify the correction process. In the parameterization, a suite of radiative transfer simulations is run prior to correction (as opposed to at each time step) to retrieve $\tau$ for a range of humidities and path lengths. T\textsubscript{surf} and T\textsubscript{air} are held constant in these simulations as they have a relatively small effect on $\tau$. Simulations for path lengths from 1 to 100 \si{\meter} and water vapor mass densities from 0.1 to 23.5 \si{\gram\per\meter\cubed} are included in Appendix \ref{appendixa}. Sensor-surface geometry is approximated as a single view factor weighted, azimuthally averaged surface-sensor path length calculated using the surface-sensor-sun urban model \citep{Soux2004} and a simplified DBM. This path length represents the average distance from the sensor to the surface as "seen" by the sensor. For each time step, measured humidity is used to infer a hemispherical transmittance ($\overline{\tau_{\Phi}}$) for the approximated surface-sensor geometry. A parameterized T\textsubscript{hem, r} can then be calculated by using measured (in this case, profile averaged) T\textsubscript{air} to decompose measured L\textsubscript{up} into irradiance received by the sensor from the surface $L_{surf}^{at-sensor}$ and from the atmosphere $L_{atm}^{at-sensor}$ via,

\begin{equation}
	\label{para}
	T_{hem, ~para} =\left(\displaystyle\frac{\biggl(\cfrac{\displaystyle L_{surf}^{at-sensor}}{ \displaystyle\tau}\biggr)}{ \displaystyle\sigma}\right)^{0.25}
\end{equation}
\noindent where $\tau$ is calculated using a radiative transfer code and a we and $L_{surf}^{at-sensor}$ is the fraction of ,

\begin{equation}
	\label{para2}
	\displaystyle L_{surf}^{at-sensor} = L_{total}^{at-sensor} - (1-\tau)\sigma T_{air}^4
\end{equation}

Using this parameterization, a climatology of T\textsubscript{hem, para} for a given surface geometry can be retrieved from approximately 100 simulations as opposed to the many millions needed for full hemispherical radiative transfer simulation. A variety of online and offline, open and closed source resources are available for radiative transfer simulation \citep{Gastellu-Etchegorry1996,Berk1987,Buehler2005}, some of which are available for free or at a low cost (Spectral-Calc), all of which are likely to provide similar results to those included in Appendix \ref{appendixa}.

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,
	height=7in,
	keepaspectratio]{para_eval}
	\caption{Modeled T\textsubscript{hem, r} versus T\textsubscript{hem, r} derived via the parameterization scheme.}
	\label{para_eval}
\end{figure}

\begin{table}[H]
 	\centering
 	\caption{Statistical performance of T\textsubscript{hem} derived using the parameterization scheme relative to modeled T\textsubscript{hem,r}. RMSE\textit{\textsubscript{s}} and RMSE\textit{\textsubscript{u}} represent the systemic and unsystematic RMSE respectively. n = 853}
 	\label{parastats}
 	\begin{tabular}{lcl}
 		\toprule 
 		Statistic & Parameterization & Citation \\  \midrule
 		Slope & 1.058 &  \\ 
 		Intercept, (\si{\kelvin}) & -1.488 &   \\ 
 		\textit{R\textsuperscript{2}} & 0.991 & \\ 
 		MAE,  (\si{\kelvin}) & 0.607& \citep{Willmott1985a} \\ 
 		RMSE,  (\si{\kelvin}) & 0.757 & \citep{Willmott1985a} \\ 
 		RMSE\textit{\textsubscript{s}},  (\si{\kelvin}) & 0.476  & \citep{Willmott1985a} \\ 
 		RMSE\textit{\textsubscript{u}},  (\si{\kelvin}) & 0.588  & \citep{Willmott1985a} \\ 
 		\textit{d}, agreement index & 0.998 & \citep{Willmott2012} \\
 		\bottomrule
 	\end{tabular} 
\end{table}

@@

\cleardoublepage 
\phantomsection  
\renewcommand*{\bibname}{References}
\addcontentsline{toc}{section}{\textbf{References}}

\putbib
\end{bibunit}
